Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-05 WSSSPE3/report/wg_main_user_community.tex
Update wg_main_user_community.tex
added some related activities

\subsubsection{Fit with related activities}
\todo{short text here - can include links/cites}

>>>>

\subsubsection{Fit with related activities}
%\todo{short text here - can include links/cites}

Mozilla Science maintains a "'Working Open' Project Guide" (http://mozillascience.github.io/leadership-training). From the introduction:
\begin{quote}
Working openly with contributors enables your
    community to learn how to build and collaborate together. This
    document is a guideline on how to work openly and involve others
    in your projects with Mozilla. We want to help you engage your
    community in a way that encourages contributors and builds other
    leaders.
  \end{quote}

Several books have been written about software communities:
\begin{itemize}
\item "Art of Community" by Jono Bacon. We could consider distilling this for scientific software.
